
\vspace{-4mm}
\section{Team Strength}
\vspace{-2mm}

Ashutosh is a $4^{th}$ year PhD student in Computer Science with several years of academic and industry research experience. With a strong systems background, he has over 6 publications in leading wireless systems conferences, and multiple awards including the R.T. Cheng Fellowship at UIUC. His recent work focuses on identifying liquids by analyzing wireless signals that pass through them, while his past work has centered around localization using multi-modal sensor fusion.

%Ashutosh is a 4th year PhD student in Computer Science with several years of
%academic and industry research experience in building wireless and mobile sensing
%systems. He is an excellent systems builder and has over 6 publications in top
%wireless systems conferences and multiple awards including the R.T.
%Cheng Fellowship. His recent work focuses on using cheap off-the-self
%wireless sensors for Liquid Identification as well as sensor fusion for accurate
%localization, ranging and tracking. 

Suraj is a $2^{nd}$ year PhD student in Electrical and Computer Engineering with a background
in  signal and image processing, wireless communications and algorithms. His recent
work focused on designing mmWave networks that enable dense spatial reuse, and currently he is working on desiging mmWave imaging systems for self driving cars. He has 3 papers under submission and has won the
Cargill Global Scholarship during his undergraduate studies. 


%his currently working on desiging mmWave imaging systems for self driving cars. 
Both Ashutosh and Suraj graduated from IIT Bombay. Their CS and ECE skills compliment each other, which will enable them to see this project through to completion. They are both part of the Systems and Networking Research Group (SyNRG) at UIUC. The group is led by 
Prof. Haitham Hassanieh and Romit Roy Choudhury, who have a long track record
in designing and build wirelss sensing and communication systems. See group website
for more details: http://synrg.csl.illinois.edu/.
